---
title: "Lab 01 - Hello R"
author: "Alexander Connolly"
date: "1/20/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```


### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Add code and narrative as needed.
Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.



```{r plot-star}
star_data <- datasaurus_dozen %>%
filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x=y, y=y)) +
geom_point()

```



```{r cor-star}
star_data %>%
summarize(r=cor(x,y))
```
R(star) = -.0629611 vs
R(dino) = -.06447185

They are almost the same!

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data=circle_data, mapping =aes(x=y, y=y)) +geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r=cor(x,y))
```
r(circle) = -.06834336 vs
r(dino) = -.06447185

They are almost the same!

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
